---
title: "Description of the file"
author: "Lounès AÏT KARROU & Jinane AMAL"
format: html
editor: visual
---
# I. Link to the GitHub project
   
Click [here](https://github.com/jinane1amal/tourismdata.git) to access to our GitHub project.   

# II. Loading the data
```{r}
#| message: false
library(here)
library(dplyr)
library(tidyr)
library(ggplot2)
theme_set(theme_bw())
here::i_am("tourismdata.Rproj")
```
   
```{r}
Arrivals<-read.csv("Datas/arrivals.csv",sep=";")
AvgExpenditures<-read.csv("Datas/avexpinttourists.csv",sep=";")
FoodExpenditures<-read.csv("Datas/foodexp.csv",sep=";")
GDP<-read.csv("Datas/gdppercap.csv",sep=";")
Gini<-read.csv("Datas/gini.csv",sep=";")
Happy<-read.csv("Datas/happinessladder.csv",sep=";")
NatDisasters<-read.csv("Datas/naturaldisasters.csv",sep=";")
Forest<-read.csv("Datas/propofprotectedforests.csv",sep=";")
```

# III. Link to our sources
You can have access tot the source of our data by clicking on the name of the variable :   
   
- [Natural disaster](https://ourworldindata.org/natural-disasters)
- [Gross Domestic Product per capita](https://ourworldindata.org/economic-growth#all-charts)
- [Gini Coefficient](https://ourworldindata.org/grapher/economic-inequality-gini-index)
- [Number of arrivals](https://data.worldbank.org/indicator/ST.INT.ARVL?end=2020&most_recent_year_desc=false&start=2020&view=bar)
- [Happiness and life satisfaction](https://ourworldindata.org/happiness-and-life-satisfaction)
- [Food expenditure](https://ourworldindata.org/grapher/food-expenditure-per-person-per-year?tab=table)
- []
-   

   
# IV. Description of our data
## A) Natural disaster
Here, we give the annual number of deaths from disaster

